2H qSIP Calculations

### 2022-03-16 qSIP_calculations.Rmd
added su_d calculation

# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

## Separate analytes and standards

```{r}
# Analytes
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  # Don't want our standard compounds to be used for generation time calculations! x_x
  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
  left_join(F_L_2F, by = "terrain")

@@

# 23:0 and 21:0 PC standard errors at inc time zero
# Determines our standard error in FAME measurements at F_0
sF_0 <- peaks_mapped_with_zeros_standards %>% 
  # Select only 21 and 23 PC standards at initial time point
  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
         inc_time_d == 0) %>%
  group_by(compound) %>% 
  summarize(F_0_at2H_mn = mean(at2H),
            F_0_at2H_se = sd(at2H))

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = `2F_alk`, # use PAME-corrected 2F value
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t # change in time
                  ),
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

>>>>

# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
source(file.path("libs", "error_prop.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

## Separate analytes and standards, calculate F_0 se

```{r}
# Analytes
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  # Don't want our standard compounds to be used for generation time calculations! x_x
  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
  # Also don't want our yeast-extract stimulated condition in our analyte pool
  filter(str_detect(sample_id, "t0t", negate = TRUE)) %>% 
  left_join(F_L_2F, by = "terrain")

@@

# 23:0 and 21:0 PC standard errors at inc time zero
# Determines our standard error in FAME measurements at F_0
sF_0 <- peaks_mapped_with_zeros_standards %>% 
  # Select only 21 and 23 PC standards at initial time point
  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
         inc_time_d == 0) %>%
  # Calculate mean and se of all 21:0 and 23:0 standard at2H values
  ungroup() %>% 
  summarize(F_0_at2H_mn = mean(at2H),
            F_0_at2H_se = sd(at2H))

# Add sF_0 to analyte data

peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_analytes %>% 
  mutate(F_0_at2H_se = 
           sF_0 %>% pull(F_0_at2H_se)
         )
```

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  mutate(
    # Explicitly define incubation parameters:
    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = `2F_alk`, # use PAME-corrected 2F value

    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t # change in time
                  ),
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),

    # Calculate uncertainty in turnover rate
    su_d = calculate_sigma_mu(
      # Mean values:
      a = a,
      F_L = f_label,
      F_T = f_t,
      F_0 = f_start,
      t = d_t,
      # Uncertainties:
      sF_0 = F_0_at2H_se,
      sF_L = F_label_se,
      sF_T = 0,
      sa = 0,
    )

  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

## Combine experimental replicates
